Moral Foundations of U.S. Political News Organizations

### 2019-04-13 pilot_manuscript erin test.Rmd
LOOK AT THIS SHIT

knitr::opts_chunk$set(cache = TRUE)
options(tinytex.verbose = TRUE)
```

@@

## Descriptive Statistics

```{r exp1sourcedescriptives, results = 'asis', echo = FALSE, message = F}

@@

tapply(final$valenceavg, final$Source, mean)
tapply(final$valenceavg, final$Source, sd)
tapply(final$wordcount, final$Source, mean)
tapply(final$wordcount, final$Source, sd)
tapply(final$uniquewords, final$Source, mean)
tapply(final$uniquewords, final$Source, sd)
tapply(final$Source, final$Source, length)
tapply(final$wordcount, final$Source, sum)

@@

tableprint[ , 1] = unique(final$Source)
tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
tableprint[ , 4] = tapply(final$X, final$Source, length)
tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
tableprint[ , 10] = tapply(final$FK, final$Source, mean)
tableprint[ , 11] = tapply(final$FK, final$Source, sd)

#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
          #caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6))
          )

The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English. Statistics calculated included *z*-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source. Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula. Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty. The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975]. For example, a text with a readability score of 11 should be easily read by a high school junior.

As seen in Table 1, the sources are similar in some aspects yet different in others. Valence appears to be slightly positive across all sources. The standard deviations seem to indicate little to no presence of a difference in valence. 
*The New York Times* published the greatest number of articles as well as total words. *Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles. Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words. Once again the standard deviations call into question any apparent differences between sources. Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable. This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*. As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.

## Inferential Statistics

To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data. MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006]. Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.

The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations. The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources. Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 2. To interpret the weighted scores, one can examine the mean and standard deviations for each. A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered. Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD. Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used). Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text. Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.

```{r exp1-table, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

#calculate d
#harm
harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
                 a = .05)

#fair
fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
                 a = .05)

#ingroup
ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
                 a = .05)

#authority
authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
                 a = .05)

#purity
purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
                 a = .05)

#put in the numbers
tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)
tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d$d)
tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d$d)
tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d$d)
tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d$d)

tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))

apa_table(tableprint,
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          #caption = "Experiment 1 Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```

```{r conference-pic, eval = F, include = F}
library(ggplot2)
library(reshape)

cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 10))

graphdata = as.data.frame(tableprint)
graphlong = melt(graphdata[ , c(1,2,4)], 
                 id = "Foundation")
graphlong2 = melt(graphdata[ , c(1, 3,5)],
                  id = "Foundation",
                  measured = c("SD_C", "SD_L"))
graphlong$sd = graphlong2$value
graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))

graphlong$value = as.numeric(as.character(graphlong$value))

graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) + 
  geom_point(position = position_dodge(width = 0.90)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(width = 0.90),
                width = .2) + 
  cleanup +
  ylab("Mean Weighted Valence") + 
  scale_color_manual(values = c("red", "blue"),
                       labels = c("Conservative", "Liberal"),
                       name = "Party") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  geom_hline(yintercept = 0, linetype = 1, color = "black")

tiff(filename = "exp1_graph.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data)
dev.off()

The results obtained in Experiment 1 did not confirm the hypothesis. The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement. The strongest effect found was for the *authority/respect* foundation owing to the fact its Cohen's *d* value was greater than the other four foundations. However, the effect was in the opposite direction of that which was hypothesized. Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives. This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research. It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.

Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis. The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content. Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary. In short, the range of topics covered in Experiment 1 was likely too broad. The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.

Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2. Generally speaking, the researchers believe their methodology to be sound. Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis. Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence. The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed. Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.

While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies. The researchers identified two such changes that were subsequently employed in Experiment 2. First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1. Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S. politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S. Supreme Court. In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.

# Experiment 2

## Kavanaugh Supreme Court Hearing

In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice. Kavanaugh was previously on the U.S. Court of Appeals for the District of Columbia. The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b]. Following allegations of sexual assault by high school classmate Dr. Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].

The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals. The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns. On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution. Kavanaugh's confirmation creates a conservative stronghold among the justices on the court. Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds. Concerns around abortion might be related either to *harm/care* or *purity/sanctity*. On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals. Likewise, arguments could be made that relate concerns regarding sexual violence to *harm/care* or *fairness/reciprocity*. Additionally, the moral duty of the Senate as the upper chamber in the U.S. legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.

## U.S. Government Shutdown of 2018-2019

The U.S. Federal Government partially shut down on December 22, 2018. The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019]. The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall. President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019]. Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].

The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place. President Trump signed the bill, ending the longest govenrment shutdown in U.S. history [@Axelrod2019]. Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole [@Kheel2019]. Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed [@Peoples2019]. While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.

As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall. Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension. As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns [@Martin2019]. Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God. Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people [@Martin2019]. This example potentially ties into the five moral foundations. Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*. In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S. could also elicit moral concerns related to *ingroup/outgroup*.

Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory. In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.

In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses. For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown. News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown. The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news. Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019). The content will be analyzed for valence and moral alignment under Moral Foundations Theory.

```{r NYTimes_kav, eval = F, include = F}

library(rvest)
library(RSelenium)

rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#page for NYTIMES
url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'

#navigate to it
remDr$navigate(url)

#click the button 
#don't change class name
#right click --> inspect element 
webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")

#with 752 results at 10 per page we need
#752 - 10 original = 742 / 10 per click = 75 clicks

for (i in 1:75) { #change this to 75 later
  webElem$clickElement()
  Sys.sleep(runif(1, 1, 5))
}

webpage <-remDr$getPageSource()

#Reading the HTML code from the website - headlines
webpage2 <- read_html(unlist(webpage))

headline_data = html_nodes(webpage2,'a')

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = urlslist[grep("/2018", urlslist)]
urlslist = unique(urlslist)
urlslist

#paste NY on front
urlslist = paste("https://www.nytimes.com", urlslist, sep = "")

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')

  ##save the data
  NYtimesDF$Source[i] = "NY Times"
  NYtimesDF$Url[i] = urlslist[i]
  NYtimesDF$Text[i] = paste(text_data, collapse = "")
  Sys.sleep(runif(1, 1, 10)) #don't make them angry
} ##end for loop

write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

```{r NYTimes_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#page for NYTIMES
url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'

#navigate to it
remDr$navigate(url)

#click the button 
#don't change class name
#right click --> inspect element 
webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")

#with 803 results at 10 per page we need
#803 - 10 original / 10 per click is 80 clicks

for (i in 1:80) {
  webElem$clickElement()
  Sys.sleep(runif(1, 1, 5))
}

webpage <-remDr$getPageSource()

#Reading the HTML code from the website - headlines
webpage2 <- read_html(unlist(webpage))

headline_data = html_nodes(webpage2,'a')

attr_data = html_attrs(headline_data) 
#attr_data

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = urlslist[grep("/201", urlslist)]
urlslist = unique(urlslist)
urlslist

#paste NY on front
urlslist = paste("https://www.nytimes.com", urlslist, sep = "")

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')

  ##save the data
  NYtimesDF$Source[i] = "NY Times"
  NYtimesDF$Url[i] = urlslist[i]
  NYtimesDF$Text[i] = paste(text_data, collapse = "")
  Sys.sleep(runif(1, 1, 10)) #don't make them angry
} ##end for loop

write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
beep(sound = 5)

remDr$close()
# stop the selenium server
rD[["server"]]$stop()
```

````{r NPR_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:50) { ##change this to 50

  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)

  #navigate to it
  remDr$navigate(url)

  #scroll on the page
  webscroll <- remDr$findElement("css", "body")
  webscroll$sendKeysToElement(list(key = "end"))

  #get the links
  webElems <- remDr$findElements(using = "css", "[href]")
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

} #close the loop

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

urlslist = unlist(urlslist_final)
#find all the ones with /2018/
urlslist2 = urlslist[grep("/2018", urlslist)]
urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
urlslist2 = unique(urlslist2)
temp = strsplit(urlslist2, split = "/")
temp2 = plyr::ldply(temp, rbind)
temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)

#deal with the ones with extra parts
temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]

#pull only the right dates
rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
                ])

urlslist3 = urlslist2[as.numeric(rows)]

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist3[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(NPRDF, "NPR_kav.csv", row.names = F)

```{r NPR_shut, eval = F, include = F}

library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

##loop through the page number at the end until done with ~3316 / 20 = 166
for (i in 1:166) {

  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)

  #navigate to it
  remDr$navigate(url)

  #scroll on the page
  webscroll <- remDr$findElement("css", "body")
  webscroll$sendKeysToElement(list(key = "end"))

  #get the links
  webElems <- remDr$findElements(using = "css", "[href]")
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

} #close the loop

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

urlslist = unlist(urlslist_final)
#find all the ones with /2018/
urlslist2 = urlslist[grep("/201", urlslist)]
urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
urlslist2 = unique(urlslist2)
temp = strsplit(urlslist2, split = "/")
temp2 = plyr::ldply(temp, rbind)
temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)

#deal with the ones with extra parts
temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]

#pull only the right dates
rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
                         (
                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
                           ), #before feb 8
                ])

urlslist3 = urlslist2[as.numeric(rows)]

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

##for loops
for (i in 315:length(urlslist3)){

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist3[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(NPRDF, "NPR_gs.csv", row.names = F)
```

````{r Slate_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"

remDr$navigate(url)

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#appear to be 10 pages
for (i in 1:10){

  #find the button to click on 
  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")

  #don't go too fast for the page to load
  Sys.sleep(runif(1, 1, 5))

  #click on the page number
  webClick[[i]]$clickElement()

  #page reload
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones with /2018/
urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
urlslist2 = unique(urlslist2)

#71 articles seems suspiciously low, so also scraped this page
#https://slate.com/tag/brett-kavanaugh/

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#337 / 20 = 17 pages
for (i in 1:17){

  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)

  remDr$navigate(url)

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones with /2018/
urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
urlslist2.1 = unique(urlslist2.1)

urlslist3 = unique(c(urlslist2, urlslist2.1))

##start a data frame
SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(SLATEDF) = c("Source", "Url", "Text")
SLATEDF = as.data.frame(SLATEDF)

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'.slate-paragraph')

  ##save the data
  SLATEDF$Source[i] = "SLATE"
  SLATEDF$Url[i] = urlslist3[i]
  SLATEDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)

```{r SLATE_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

url = "https://slate.com/search?q=government+shutdown"

remDr$navigate(url)

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#appear to be 10 pages
for (i in 1:10){

  #find the button to click on 
  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")

  #don't go too fast for the page to load
  Sys.sleep(runif(1, 1, 5))

  #click on the page number
  webClick[[i]]$clickElement()

  #page reload
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

>>>>

knitr::opts_chunk$set(cache = TRUE)
```

@@

```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}

@@

# tapply(final$valenceavg, final$Source, mean)
# tapply(final$valenceavg, final$Source, sd)
# tapply(final$wordcount, final$Source, mean)
# tapply(final$wordcount, final$Source, sd)
# tapply(final$uniquewords, final$Source, mean)
# tapply(final$uniquewords, final$Source, sd)
# tapply(final$Source, final$Source, length)
# tapply(final$wordcount, final$Source, sum)

@@

tableprint[ , 1] = unique(final$Source)
tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
tableprint[ , 4] = tapply(final$X, final$Source, length)
tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
tableprint[ , 10] = tapply(final$FK, final$Source, mean)
tableprint[ , 11] = tapply(final$FK, final$Source, sd)
```

```{r temp, results = 'asis', eval = T, echo = F}
#change this to match

tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))

apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
          caption = "Experiment 1 - Descriptive Statistics by Source",
          format = "latex",
          small = T,
          escape = F,
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"))
```
